Bayes Exploration with Brms

### 2023-08-11 Analysis/data_organize.qmd
google sync update

@@

```{r}
#| eval: false
e1 <- d |> filter(fb=="Continuous" & bandOrder=="Original")
e2 <- d |> filter(fb=="Continuous" & bandOrder=="Reverse")
e3 <- d |> filter(fb=="Ordinal")

date.append="07-27-23"

>>>>

d <- d |> mutate(Exp=case_when(
  fb=="Continuous" & bandOrder=="Original" ~ "E1",
  fb=="Continuous" & bandOrder=="Reverse" ~ "E2",
  fb=="Ordinal" ~ "E3",
  TRUE ~ NA_character_
))

d <- d |> mutate(vxC = ifelse(vx>1800,1800,vx))
d <- d %>% relocate(vxC,.after=vx)
d <- d |> select(-goodThrow, -trainVec, -fullCond)

@@

```{r}
#| eval: false
e1 <- d |> filter(fb=="Continuous" & bandOrder=="Original") |> mutate(id=factor(id,levels=unique(id)))
e2 <- d |> filter(fb=="Continuous" & bandOrder=="Reverse") |> mutate(id=factor(id,levels=unique(id)))
e3 <- d |> filter(fb=="Ordinal") |> mutate(id=factor(id,levels=unique(id)))

date.append="08-04-23"

### 2023-08-11 Misc/htw_dp.qmd
google sync update

---
title: "Project 2"
subtitle: " Variability and Function Learning "
bibliography: "../Bib/HTW.bib"
date: last-modified
keep-tex: true
code-fold: true
---

>>>>

---
title: "Project 2"
subtitle: " Variability and Function Learning "
bibliography: "../Assets/Bib/HTW.bib"
date: last-modified
keep-tex: true
code-fold: true
---

### 2023-08-11 Misc/scratch/bayes_explore.qmd
extremely minor organization
google sync update

test <- e1 |> 
  filter(expMode2 == "Test")  
 test <- test |> mutate(id=factor(id,levels=unique(id)),
         vxbn=vxb/max(test$vxb),vxn=vx/max(test$vx),bandIntn=bandInt/max(test$vx),bandIntnb=bandInt/max(test$vxb),svx=scale(vx, scale = TRUE),
         vxC=ifelse(vx>2000,2000,vx))

@@

Unrealistic priors
```{r}
#| eval: false

fit_int_unif <- brm(vx ~ 1, # 170.4 sec execution time with 8 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(uniform(-10^6, 10^6),
          class = Intercept,
          lb = -10^6,
          ub = 10^6),
    prior(uniform(0, 10^6),
          class = sigma,
          lb = 0,
          ub = 10^6)
  ),
  iter = 3000,
  control = list(adapt_delta = .99,
                 max_treedepth = 15),
  file="cache/fit_int_unif"
)

fit_int_unif

```
 Family: gaussian 
  Links: mu = identity; sigma = identity 
Formula: vx ~ 1 
   Data: test (Number of observations: 10109) 
  Draws: 4 chains, each with iter = 3000; warmup = 1500; thin = 1;
         total post-warmup draws = 6000

Population-Level Effects: 
          Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
Intercept   835.95      4.45   827.48   844.81 1.00     3927     2927

Family Specific Parameters: 
      Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
sigma   435.94      3.30   429.37   442.35 1.01      487      576

@@

@@

>>>>

test <- e1 |> filter(expMode2 == "Test")

 test <- test |> mutate(id=factor(id,levels=unique(id)),
         vxbn=vxb/max(test$vxb),vxn=vx/max(test$vx),bandIntn=bandInt/max(test$vx),bandIntnb=bandInt/max(test$vxb),svx=scale(vx, scale = TRUE),
         vxC=ifelse(vx>2000,2000,vx))

@@

fit_int_norm <- brm(vx ~ 1+bandInt+(1|id), # 2.1 sec execution time with 4 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(800, 10), class = Intercept),
    prior(normal(400, 10), class = sigma)
  )
)
bayesplot::ppc_dens_overlay_grouped(test$vx,
  yrep = posterior_predict(fit_int_norm, ndraws = 100),
  group = test$bandInt
)

bandId_norm_vxC <- brm(vxC ~ 1+bandInt+(1|id), # 2.1 sec execution time with 4 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(800, 10), class = Intercept),
    prior(normal(400, 10), class = sigma)
  )
)

bayesplot::ppc_dens_overlay_grouped(test$vx,
  yrep = posterior_predict(bandId_norm_vxC, ndraws = 100),
  group = test$bandInt
)
```

loo_fit<- loo(fit_int_norm,bandId_norm_vxC)
loo_fit$diffs %>% as.data.frame() %>% round(1)

loo_R2(fit_int_norm)
loo_R2(bandId_norm_vxC)

loo_comp <- loo_compare(list(vx = loo(fit_int_norm), 
                             vxC = loo(bandId_norm_vxC)))
loo_comp
1 - pnorm(-loo_comp[2,1], loo_comp[2,2])

@@

test_int_vx <- run_model(brm(vx~1,data=test),modelName = "test_int_vx")
test_int_vx3 <- brm(vx~1,data=test,file=paste0(here::here("data/model_cache"),"/test_int_vx"))

@@

IRT style
```{r}

fit_b_irt <- brm(vxC ~ 1+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
fit_b_irt

coef(fit_b_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)
coef(fit_b_irt)$bandInt %>% as_tibble(rownames="bandInt")

fit_dist_irt <- brm(dist ~ 1+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
fit_dist_irt
coef(fit_dist_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)
coef(fit_dist_irt)$bandInt %>% as_tibble(rownames="bandInt")

fit_distCondit_irt <- brm(dist ~ 1+condit+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
coef(fit_distCondit_irt)$bandInt %>% as_tibble(rownames="bandInt") 
coef(fit_distCondit_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)

```
coef(fit_b_irt)$bandInt %>% as_tibble(rownames="bandInt")

bandInt Estimate.Intercept Est.Error.Intercept Q2.5.Intercept Q97.5.Intercept
  <chr>                <dbl>               <dbl>          <dbl>           <dbl>
1 100                   595.                18.7           560.            633.
2 350                   716.                18.8           680.            754.
3 600                   826.                18.7           789.            863.
4 800                  1023.                20.1           984.           1064.
5 1000                 1167.                20.2          1128.           1207.
6 1200                 1260.                20.5          1220.           1299.

coef(fit_dist_irt)$bandInt %>% as_tibble(rownames="bandInt") 
# A tibble: 6 × 5
  bandInt Estimate.Intercept Est.Error.Intercept Q2.5.Intercept Q97.5.Intercept
  <chr>                <dbl>               <dbl>          <dbl>           <dbl>
1 100                   326.                13.7           300.            354.
2 350                   243.                13.7           217.            271.
3 600                   195.                13.7           169.            222.
4 800                   207.                15.0           178.            237.
5 1000                  227.                15.2           197.            256.
6 1200                  269.                15.3           240.            300.
